SHARP - II. Mass structure in strong lenses is not necessarily substructure: A flux ratio anomaly from an edge-on disc

### 2016-02-23 papers/B1555_EdgeOn/B1555_letter.tex
Small changes to manuscript text

\textbf{We use {\sc gravlens} to obtain the best-fit SIE+ExpDisc lens model. The best-fit parameters from \citet{Marlow99} are set as the starting point of the SIE profile. By looking at the NICMOS F160W imaging, which has the highest signal-to-noise ratio of disc among the data, we fix the centroid position as $(-0.162, -0.206)$ , ellipticity as $e=0.83$, and position angle of $\theta=8^\circ$. The total number of free parameters is 9. After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain uncertainties.}

The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c. Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).  In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass. Studies on edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent mass in the Einstein radius \citep{swells1,swells3,swells6}.} 
%In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy. 
%We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.

@@

Here, we find evidence for an edge-on disc in the flux-ratio anomaly
gravitational lens B1555+375 that can account for the required
perturbation in the mass model.  \textbf{Although the constraint on disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in AO imaging and the lack of redshift information, our model indicates that the flux anomalies in B1555+375, at least, have strong link to the present of its edge-on disc. } Such
high-order deviations from a smooth mass distribution have already
been suggested previously \citep{evans03, congdon05}, but this is the
first time that an observed disc has been explicitly modelled to
account for a flux-ratio anomaly. However, it is important to realise
that by including observationally-motivated modifications to a
`smooth' mass distribution, such as luminous dwarf companions or
edge-on discs, in the mass models, we are still limited in our
interpretation if we can not determine how much of the anomalies are
due to these components. For our current analysis of B1555+375, we
have shown that the entire anomaly could be caused by the edge-on
disc. \textbf{Some of concerns may arise that an overestimated disc component leads to a model can explain the entire anomaly. One is saying can a spiral lens with massive disc not distort the arc close to the disc. J0820+4847, one of the SWELLS samples, is an edge-on lens has an arc right across its disc. The SWELLS studies indicate it has 15 per cent of disc mass within the Einstein radius. Other SWELLS lenses have disc mass fraction range from 5 per cent to 30 per cent \citep{swells1,swells3,swells6}. These numbers tell that the disc in our best-fit model of B1555+375 still fits into the nature of general spiral lenses.}  However, it may be possible to independently constrain the mass
of the disc through kinematic measurements (most likely from
mm-wavelength resolved emission line observations), which would test
whether the disc actually makes a sufficient contribution to the mass
model \citep[e.g. as in the case of B1933+503;][]{suyu12}. Also, in
the blue contours of Fig.~\ref{fig:3panel}a, B1555+375 shows evidence
for an extended $\sim$ 100 mas gravitational arc at radio wavelengths
that crosses the edge-on disc. Further high resolution imaging with
very long baseline interferometry will provide the observational
constraints required to fully test whether the disc is sufficient to
cause the anomaly.

>>>>

\textbf{We use {\sc gravlens} to obtain the best-fit SIE+ExpDisc lens model. The best-fit parameters from \citet{Marlow99} are chosen as the starting point of the SIE profile. We have used the NICMOS F160W imaging, in which the disc component has the highest signal-to-noise ratio amongst our data, to fix the centroid position to $(-0.162, -0.206)$, the ellipticity to $e=0.83$, and the position angle to $\theta=8^\circ$. The total number of free parameters is 9. After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain uncertainties.}

The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c. Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the \textbf{ExpDisc component make up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).  In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass. Investigations of edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent of the mass within the Einstein radius \citep{swells1,swells3,swells6}.} 
%In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy. 
%We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.

@@

Here, we find evidence for an edge-on disc in the flux-ratio anomaly
gravitational lens B1555+375 that can account for the required
perturbation in the mass model.  \textbf{Although a constraint on the disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomalies in B1555+375, at least, have a strong link to the presence of its edge-on disc. } Such
high-order deviations from a smooth mass distribution have already
been suggested previously \citep{evans03, congdon05}, but this is the
first time that an observed disc has been explicitly modelled to
account for a flux-ratio anomaly. However, it is important to realise
that by including observationally-motivated modifications to a
`smooth' mass distribution, such as luminous dwarf companions or
edge-on discs, in the mass models, we are still limited in our
interpretation if we can not determine how much of the anomalies are
due to these components. For our current analysis of B1555+375, we
have shown that the entire anomaly could be caused by the edge-on
disc. \textbf{Some of concerns may arise that an overestimated disc component leads to a model can explain the entire anomaly. One is saying can a spiral lens with massive disc not distort the arc close to the disc. J0820+4847, one of the SWELLS samples, is an edge-on lens has an arc right across its disc. The SWELLS studies indicate it has 15 per cent of disc mass within the Einstein radius. Other SWELLS lenses have disc mass fraction range from 5 per cent to 30 per cent \citep{swells1,swells3,swells6}. These numbers tell that the disc in our best-fit model of B1555+375 still fits into the nature of general spiral lenses.}  However, it may be possible to independently constrain the mass
of the disc through kinematic measurements (most likely from
mm-wavelength resolved emission line observations), which would test
whether the disc actually makes a sufficient contribution to the mass
model \citep[e.g. as in the case of B1933+503;][]{suyu12}. Also, in
the blue contours of Fig.~\ref{fig:3panel}a, B1555+375 shows evidence
for an extended $\sim$ 100 mas gravitational arc at radio wavelengths
that crosses the edge-on disc. Further high resolution imaging with
very long baseline interferometry will provide the observational
constraints required to fully test whether the disc is sufficient to
cause the anomaly.
